---
title: "Numerical analysis"
output:
  html_document:
    df_print: paged
---
```{r}
#install.packages('combinat')
library(combinat)
```

Using formula (1) for calculting probability of stategy Sn on N sequence, we create proper function
```{r}
Probability_of_Sn <- function(n,N){
  k = N-1
  p = (n/N)*sum(1/(n : k))
  return (p)
}
Probability_of_Sn(1,4)
```

Here we create algorithms of stratege Sn (skip first n elements in sequence, and look for element that bigger than first n numbers )
```{r}
Sn_Algorithms_ <- function(n,c){
  if(n == 0){
    return(c[1])
  }
  for (number in c[-(1:n)]){
    if (number > max(c[1:n])){
      return(number)
    }
  }
  return(tail(c, n = 1))
}
s=c(6,2,1,4)
Sn_Algorithms_(2,s)

```

Function that represents success of choosing max element
```{r}
Desicion_sucess <- function(n,c){
  result = Sn_Algorithms_(n,c)
  if (result == max(c)){
    return(1)
  } else {
    return(0)
    }
  
}
```


Functions for calculating sample probability of success(with different conditions)
```{r}
probability <- function(n,N) {
  sum = 0
  for (i in 0:1000){
    c = sample(N,N, replace = FALSE)
    sum = sum + Desicion_sucess(n,c)
  }
  return (sum / 1000)
}
probability_replacement <- function(n,N) {
  sum = 0
  for (i in 0:1000){
    c = sample(N,N, replace = T)
    sum = sum + Desicion_sucess(n,c)
  }
  return (sum / 1000)
}
probability(1,4)
```
Find opimal n strategy for every sequence  N {1:20}
```{r}
r<-c(0)
for ( i in 2:20){
  n<-integer()
  for (j in 0:i-1) {
    n[j]<- Probability_of_Sn(j,i)
  }
  r[i]<-which(n==max(n))
}
r

```

Table for comparing our values
```{r}
theor_prob=integer()
sample_prob=integer()
sample_prob_replacement=integer()
i=1
for (j in r){
  theor_prob[i]<-Probability_of_Sn(j,i)
  sample_prob[i]<-probability(j,i)
  sample_prob_replacement[i]<-probability_replacement(j,i)
  i=i+1
  
}
theor_prob[1] = 1
data_p <-data.frame('N' = 1:20, 'Optimal n' = r, 'Theor_Prob' = theor_prob, 'Sample_Prob' = sample_prob,'Sample_Prob(Replacement)' = sample_prob_replacement)
data_p
```
Here we calculate expectation of choise rank observing the permutations of sequence.(rank 1 - is the best)
```{r}
s <- integer()
c <- integer()
d <- integer()
for (i in 1:8) {
  n<-integer()
  perm <- permn(sample(i,i, replace = FALSE))
  for (j in 0:(i-1)){
    E<-integer()
    z=1
    for(k in perm){
      rank=Sn_Algorithms_(j,k)
      E[z]=rank
      z = z+1
    }
    n[j+1] = mean(E)
  }
  for(l in (1:length(n))){
    if (n[l] == max(n)){
      g = l
    }
  }
  c[i] = g-1
  d[i] = max(n)
}
data_e <- data.frame('N' = 1:8, 'n_that_maximimizes_choise_rank'= c,'Expected_rank' = d, 'n_for_optimal_best_choise'=r[1:8])
data_e
```
In the most cases, n that makes our choise optimal for the best candidate, gives us the worst expectaion of  choise rank. 
